MLISA: Machine Learning-based \\ Intelligent Service Agents

### 2014-11-14 papers/webservice-coalition-learning/webservice_coalition_learning.tex
changes

\subsection{Join Consequences}\label{s:jc}
It is worth mentioning that a \emph{join} event takes place as a result of two parties that are looking for expanding their collaborations. All actions are picked in attempt to enhance the overall outcome. However, the selected action may result in decreasing the overall utility in long term. This is the case where a single web service joins a community, but the complex process of task allocation eliminates the visibility of the web service and thus, the web service stays idle within the community. In other words the join action is not beneficial for the web service and in the first spot, it was a bad decision.  The same event might be beneficial for the community as it hosts a web service that in case of a relative task can engage the web service in the task. But overall, both sides do not benefit from collaborating with each other and the join event has negative consequences in at least one sides' utility.

There is another scenario, which is more common, that is the web service joins a community and both parties benefit from the join. This action is rational as both web service and the community web service enhance the utility. However, the community may not be the best possible choices for the web service for join. In other words, the web service could have joined a better community, but because of lack of knowledge about the surrounding environment, joins the available community that in fact enhances its utility. So the web service stays within the community for long term. We recognize these challenges and the proposed model (in the following section) provide solutions that effectively address the aforementioned challenges.

@@

In this section, we describe our training process and methodology that we quip web services with a decision making mechanism. In this methodology, we first present the training process and then we evaluate the learning model of web service in community settings.

@@

We used a data set that is extracted from running web services. In this data set, each web service is associated with a number of features that reflect its functionality. These web services are opertaing in an online environment and are continuously assigned with tasks to handle. Sometime, they pass tasks around distribute sub-tasks among each other and handle the task in the form of collaborative work. To engage in communities, we add additional features that reflect web service’s utility as a result of joining other web services to form a community. The additional features are computed based on two assumptions that we adopt for community to be formed. Since we have 64 different time slots of extracted features for each web service, we could build synthetic data set that contains features of large number of web services in a sequence of time. Therefore, we train a learning model that adopts the trend of joining a community and use the model to predict/find the appropriate community for testing web services. To train our model, we build a decision tree as benchmark for our decision making mechanism. The decision tree is built based on training the real data we obtain from operating web services and features we extract in regards to their performance either alone as a part of joint work with other web services. As a result, we are able to classify web services to single and joined lables and propose appropriate communities that best fit to web service’s requirements.

@@

We have adopted the web service data set provided by \cite{10.1109/ISSRE.2011.17}. The raw data provides real-world QoS evaluation results from several users on 5,825 Web services over 64 different time frames\footnote{http://www.wsdream.net/}. In this data set, each web service is associated with a number of features that reflect its functionality. By summarizing the data provided for each web service over different time slots, we have acquired three quality feature for each individual web service. There quality features are the three internal features introduced in section \ref{s:if}: \emph{throughput}, \emph{availability} and \emph{execution time}. 
%To engage in communities, we add two additional external features that reflect web services estimation of its quality metrics compared to other web services. 
Therefore, we have generated an array of web services with 3 distinct features.

>>>>

\subsection{Join Consequences}\label{s:jc}
It is worth mentioning that a \emph{join} event takes place as a result of two parties that are looking to expanding their collaborations. All actions are chosen in an attempt to enhance the overall outcome. However, the selected action may result in decreasing the overall utility in the long run. 
% long term.
This is the case when a single web service joins a community, but the complex process of task allocation eliminates the visibility of the web service and, thus, the web service stays idle within the community. In other words, the join action is not beneficial for the web service and it was a bad decision. The same event might be beneficial for the community, as it hosts a web service that, in the case of a relative task, can engage the web service in the task. But overall, neither side benefits from collaborating with the other and the join event has negative consequences for at least one side's utility.

The more common scenario is when both parties benefit from the joining of a web service with a community. This action is rational, as both the web service and the community enhance the utility. However, the community may not be the best choice for the web service to join. In other words, the web service could have joined a better community, but, due to of lack of knowledge about the surrounding environment, joined the available community , and since the community does, in fact, enhance its utility, the web service stays with that community long term. In the following section the proposed model provides solutions that effectively address the aforementioned challenges.

@@

In this section, we describe our training process and the methodology used to equip web services with a decision making mechanism. In this methodology, we first present the training process and then we evaluate the learning model for web services in community settings.

@@

We used a data set extracted from running web services. In this data set, each web service is associated with a number of features that reflect its functionality. These web services operate in an online environment and are continuously assigned tasks to handle. Sometimes, they pass tasks around, distributing sub-tasks among themselves and handling tasks in a collaborative effort. To engage in communities, we add additional features that reflect web services' utility as a result of joining other web services to form a community. The additional features are computed based on two assumptions that we adopt for a community to be formed. Since we have 64 different time slots of extracted features for each web service, we can build a synthetic data set that contains features of a large number of web services in a sequence of time. Therefore, we train a learning model that adopts the trend of joining a community and use the model to predict/find the appropriate community for other web services. To train our model, we build a decision tree as a benchmark for our decision making mechanism. The decision tree is built by training the real data obtained from operating web services and extracting features related to their performance, either alone or as part of a joint effort with other web services. As a result, we are able to classify web services as either single or joined and propose the communities that are best fitted to the web services' requirements.

@@

We have adopted the web service data set provided by \cite{10.1109/ISSRE.2011.17}. The raw data provides real-world QoS evaluation results from several users on 5,825 web services over 64 different time frames\footnote{http://www.wsdream.net/}. In this data set, each web service is associated with a number of features that reflect its functionality. By summarizing the data provided for each web service over different time slots, we have acquired three quality features for each individual web service. Their quality features are the three internal features introduced in Section \ref{s:if}: \emph{throughput}, \emph{availability} and \emph{execution time}. 
%To engage in communities, we add two additional external features that reflect web services estimation of its quality metrics compared to other web services. 
Therefore, we have generated an array of web services with three distinct features.
